Setting up Data

### 2020-02-25 doc/Results.rmd
small change to setup, more cleaning ect.

```{r MLH1.FEMALE.TABLE, echo=FALSE}

@@

```{r MLH1.MALE.TABLE, echo=FALSE}
male_MLH1mouse.av <- subset(AP_mouse_table_w.Ages, select= -c(sex.y,sex.x,
                            subsp.y,subsp.x,
                    category.y,category.x, strain.x,
                    strain.y, mouse.1  )  )

@@

@@

#there might be an issue with the algorithm performance 
#given the parrelle diagonal lines -- 
#this might be due to the dates imaged

>>>>

```{r MLH1.FEMALE.TABLE, echo=FALSE}
female_mouse.av <- subset(AP_mouse_table_w.Ages, select= -c(sex.y,sex.x,
                            subsp.y,subsp.x,
                    category.y,category.x, strain.x,
                    strain.y, mouse.1  )  )

@@

```{r MLH1.MALE.TABLE, echo=FALSE}
#AP_mouse_table.MLH1_HQ

#find the table that includes the las image data
male_MLH1mouse.av <- AP_mouse_table_w.Ages

@@

#investigating potential skew / technical effects in the algorithm

@@

median(bep$oldest.image.date) #"2017-08-03"
#there might be an issue with the algorithm performance 
#given the parrelle diagonal lines -- 
#this might be due to the dates imaged  2017-02-07

bep$date.cut.off <- ifelse( bep$oldest.image.date < "2017-02-07", 0, 1 )

Neg.control.find.date <- ggplot(bep, aes(x=mean.skel, y=mean.bin, color=strain))+geom_point()+
  scale_color_manual(values=colors_of_strains)+ggtitle("Total SC by mean CO\nMouse Means")+facet_wrap(~date.cut.off)

#there's evidence that the algorithm might have some biased effects -- 
#that will be investigated later.

### 2020-02-25 src/SetupData.Rmd
small change to setup, more cleaning ect.

#during merging -- try to just merge a few cols: 
AP_mouse_table_w.Ages <- merge(AP_mouse_table.MLH1_HQ, meta.data)
#don't use by, that makes duplicate cols
# by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two

>>>>

#during merging -- try to just merge a few cols: 
AP_mouse_table_w.Ages <- merge(AP_mouse_table.MLH1_HQ, meta.data)

#this should be transfering the image dataes!

#don't use by, that makes duplicate cols
# by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two
